Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-12 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

% Paper title.
\title{Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses an
adapted extension of the Laplace Beltrami operator. Along with the
method, this work also presents new applications in sculpting and
modeling, with subdivision of surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, whereby it performs a curvature enhancement and shape exaggeration
of the model, creating a family of different versions of the same
object and therefore preserving the detail of the original model and
a realistic appearance.

The curvature enhancement and shape exaggeration can be used in the
sculpting proccess when inflating with a brush since current brushes
that perform inflation end up by losing detail when moving vertices
\cite{Stanculescu2011}, in contrast the presented method allows inflation
of the mesh vertices by moving them towards the reverse curvature
direction, conserving the shape and sharp features of the model.

Interest on meshes composed by triangles and quads has increasing
in recent years due to the flexibility of modeling tools as Blender
3D \cite{blender}. Today many artists manually connect vertices such
that its edition allows a simple way to perform animation processes
and interpolation \cite{Mullen2007}. For these reasons it is very
important to develop an operator that allows working with this type
of mesh immediately, eliminating the need to preprocessing the mesh
to convert to triangles and losing the original design made by users.

>>>>

% Paper title.
\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhanced shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for modeling a hybrid quad/triangle
mesh by enhancing the global object curvature. This method uses an
adapted extension of the Laplace Beltrami operator. Along with the
method, this work presents new applications in sculpting and
modeling, with subdivision of surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Nevertheless,
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, whereby it performs a curvature enhancement and shape exaggeration
of the model, creating a family of different versions of the same
object and therefore preserving the detail of the original model and
a realistic appearance.

Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}. Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}. It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles. The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when brush inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}. In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.
